---
title: "SLiM analysis"
author: "Gabriel, Douhan, Léo"
date: "2024-11-28"
output: html_document
---
```{r}
library(ggplot2)
library(patchwork)
```

# Load the data

## random_mating

```{r}
# enter your directory 

path <- "C:/Users/besan/Desktop/gen p/BreedingSimulator/"


# Load random mating

rm_df <- read.table(paste0(path,"1_Outputs/1_Random-Relatedness/random-relatedness_10000burn_100gen_1_popstats.txt"), header = T)


for(i in 2:100){
  df <- read.table(paste0(path,"1_Outputs/1_Random-Relatedness/random-relatedness_10000burn_100gen_", i, "_popstats.txt"), header = T)
  rm_df <- rbind(rm_df, df)
}

rm_df$Generation <- rm_df$Generation - 10000
rm_df$PopulationID <- rep(1:100, each = 101)

# load genetic_load regime

genload_df <- read.table(paste0(path, "1_Outputs/3_Genetic-Load/genetic_load_10000burn_100gen_1_popstats.txt"), header = T)


for(i in 2:100){
  df <- read.table(paste0(path, "1_Outputs/3_Genetic-Load/genetic_load_10000burn_100gen_", i, "_popstats.txt"), header = T)
  genload_df <- rbind(genload_df, df)
}
genload_df$Generation <- genload_df$Generation - 10000
genload_df$PopulationID <- rep(1:100, each = 101)
#load relatedness model

related_df <- read.table(paste0(path,"1_Outputs/5_Relatedness_paper/relatedness_paper_10000burn_100gen_1_popstats.txt"), header = T)


for(i in 2:100){
  df <- read.table(paste0(path, "1_Outputs/5_Relatedness_paper/relatedness_paper_10000burn_100gen_", i, "_popstats.txt"), header = T)
  related_df <- rbind(related_df, df)
}

related_df$Generation <- related_df$Generation -10000
related_df$PopulationID <- rep(1:100, each = 101)
#load genetic + relatedness

mixed_df <- read.table(paste0(path, "1_Outputs/6_Mixed_paper/mixed_paper_10000burn_100gen_1_popstats.txt"), header = T)


for(i in 2:100){
  df <- read.table(paste0(path, "1_Outputs/6_Mixed_paper/mixed_paper_10000burn_100gen_", i, "_popstats.txt"), header = T)
  mixed_df <- rbind(mixed_df, df)
}
mixed_df$PopulationID <- rep(1:100, each = 101)
mixed_df$Generation <- mixed_df$Generation -10000

# Load full random mating

random_df <- read.table(paste0(path, "1_Outputs/0_Random/random_10000burn_100gen_1_popstats.txt"), header = T)


for(i in 2:100){
  df <- read.table(paste0(path, "1_Outputs/0_Random/random_10000burn_100gen_", i, "_popstats.txt"), header = T)
  random_df <- rbind(random_df, df)
}

random_df$Generation <- random_df$Generation - 10000
random_df$PopulationID <- rep(1:100, each = 101)


old_related_df <- read.table(paste0(path,"1_Outputs/2_Relatedness/relatedness_10000burn_100gen_1_popstats.txt"), header = T)


for(i in 2:100){
  df <- read.table(paste0(path, "1_Outputs/2_Relatedness/relatedness_10000burn_100gen_", i, "_popstats.txt"), header = T)
  old_related_df <- rbind(old_related_df, df)
}

old_related_df$Generation <- old_related_df$Generation -10000
old_related_df$PopulationID <- rep(1:100, each = 101)

old_mixed_df <- read.table(paste0(path,"1_Outputs/4_Mixed/mixed_10000burn_100gen_1_popstats.txt"), header = T)


for(i in 2:100){
  df <- read.table(paste0(path, "1_Outputs/4_Mixed/mixed_10000burn_100gen_", i, "_popstats.txt"), header = T)
  old_mixed_df <- rbind(old_mixed_df, df)
}

old_mixed_df$Generation <- old_mixed_df$Generation -10000
old_mixed_df$PopulationID <- rep(1:100, each = 101)
```

Now we do the mean of every replicat at each generation for genload

```{r}
heterozygo <- c()
genetic_load <- c()
realized_load <- c()
fitness <- c()
gen <- c()
for(i in 1:101){
  generation <- genload_df[genload_df$Generation == i,]
  heterozygo <- c(heterozygo, mean(generation$Heterozygosity))
  genetic_load <- c(genetic_load, mean(generation$totalLoad))
  realized_load <- c(realized_load, mean(generation$RelzLoad))
  fitness <- c(fitness, mean(generation$MeanFitness))
  gen <- c(gen, i)
}
mean_genload_df <- as.data.frame(cbind(gen, heterozygo, genetic_load, realized_load, fitness))
colnames(mean_genload_df) <- c("generation", "heterozygosity", "genetic_load", "realized_load", "fitness")
```
now for random mating

```{r}
heterozygo <- c()
genetic_load <- c()
realized_load <- c()
fitness <- c()
gen <- c()
for(i in 1:101){
  generation <- rm_df[rm_df$Generation == i,]
  heterozygo <- c(heterozygo, mean(generation$Heterozygosity))
  genetic_load <- c(genetic_load, mean(generation$totalLoad))
  realized_load <- c(realized_load, mean(generation$RelzLoad))
  fitness <- c(fitness, mean(generation$MeanFitness))
  gen <- c(gen, i)
}
mean_rm_df <- as.data.frame(cbind(gen, heterozygo, genetic_load, realized_load, fitness))
colnames(mean_rm_df) <- c("generation", "heterozygosity", "genetic_load", "realized_load", "fitness")
```

now for relatedness

```{r}
heterozygo <- c()
genetic_load <- c()
realized_load <- c()
fitness <- c()
gen <- c()
for(i in 1:101){
  generation <- related_df[related_df$Generation == i,]
  heterozygo <- c(heterozygo, mean(generation$Heterozygosity))
  genetic_load <- c(genetic_load, mean(generation$totalLoad))
  realized_load <- c(realized_load, mean(generation$RelzLoad))
  fitness <- c(fitness, mean(generation$MeanFitness))
  gen <- c(gen, i)
}
mean_related_df <- as.data.frame(cbind(gen, heterozygo, genetic_load, realized_load, fitness))
colnames(mean_related_df) <- c("generation", "heterozygosity", "genetic_load", "realized_load", "fitness")
```

olde hetero

```{r}
heterozygo <- c()
genetic_load <- c()
realized_load <- c()
fitness <- c()
gen <- c()
for(i in 1:101){
  generation <- old_related_df[old_related_df$Generation == i,]
  heterozygo <- c(heterozygo, mean(generation$Heterozygosity))
  genetic_load <- c(genetic_load, mean(generation$totalLoad))
  realized_load <- c(realized_load, mean(generation$RelzLoad))
  fitness <- c(fitness, mean(generation$MeanFitness))
  gen <- c(gen, i)
}
mean_old_related_df <- as.data.frame(cbind(gen, heterozygo, genetic_load, realized_load, fitness))
colnames(mean_old_related_df) <- c("generation", "heterozygosity", "genetic_load", "realized_load", "fitness")
```


now for mixed

```{r}
heterozygo <- c()
genetic_load <- c()
realized_load <- c()
fitness <- c()
gen <- c()
for(i in 1:101){
  generation <- mixed_df[mixed_df$Generation == i,]
  heterozygo <- c(heterozygo, mean(generation$Heterozygosity))
  genetic_load <- c(genetic_load, mean(generation$totalLoad))
  realized_load <- c(realized_load, mean(generation$RelzLoad))
  fitness <- c(fitness, mean(generation$MeanFitness))
  gen <- c(gen, i)
}
mean_mixed_df <- as.data.frame(cbind(gen, heterozygo, genetic_load, realized_load, fitness))
colnames(mean_mixed_df) <- c("generation", "heterozygosity", "genetic_load", "realized_load", "fitness")
```

old mixed
```{r}
heterozygo <- c()
genetic_load <- c()
realized_load <- c()
fitness <- c()
gen <- c()
for(i in 1:101){
  generation <- old_mixed_df[old_mixed_df$Generation == i,]
  heterozygo <- c(heterozygo, mean(generation$Heterozygosity))
  genetic_load <- c(genetic_load, mean(generation$totalLoad))
  realized_load <- c(realized_load, mean(generation$RelzLoad))
  fitness <- c(fitness, mean(generation$MeanFitness))
  gen <- c(gen, i)
}
mean_old_mixed_df <- as.data.frame(cbind(gen, heterozygo, genetic_load, realized_load, fitness))
colnames(mean_old_mixed_df) <- c("generation", "heterozygosity", "genetic_load", "realized_load", "fitness")
```


now for full random

```{r}
heterozygo <- c()
genetic_load <- c()
realized_load <- c()
fitness <- c()
gen <- c()
for(i in 1:101){
  generation <- random_df[random_df$Generation == i,]
  heterozygo <- c(heterozygo, mean(generation$Heterozygosity))
  genetic_load <- c(genetic_load, mean(generation$totalLoad))
  realized_load <- c(realized_load, mean(generation$RelzLoad))
  fitness <- c(fitness, mean(generation$MeanFitness))
  gen <- c(gen, i)
}
mean_random_df <- as.data.frame(cbind(gen, heterozygo, genetic_load, realized_load, fitness))
colnames(mean_random_df) <- c("generation", "heterozygosity", "genetic_load", "realized_load", "fitness")
```


```{r}
realized_graph <- ggplot() + geom_line(data = mean_genload_df, aes(x = generation, y = realized_load), color = "indianred1", size = 1 ) +  geom_line(data = mean_rm_df, aes(x = generation, y = realized_load), color = "orchid1", size = 1 ) + geom_line(data = mean_random_df, aes(x = generation, y = realized_load), color = "yellow1", size = 1 )+ geom_line(data = mean_related_df, aes(x = generation, y = realized_load), color = "skyblue1", size = 1 )+ geom_line(data = mean_mixed_df, aes(x = generation, y = realized_load), color = "olivedrab3", size = 1 ) + labs(x = "Generations", y = "Realized load") + 
  theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 30),  # X-axis title size
    axis.title.y = element_text(size = 30),
    axis.text.x = element_text(size = 20),  # Increase x-axis label size
    axis.text.y = element_text(size = 20)# Increase axis title siz
  )

load_graph <- ggplot() + geom_line(data = mean_genload_df, aes(x = generation, y = genetic_load), color = "indianred1", size = 1 ) +  geom_line(data = mean_rm_df, aes(x = generation, y = genetic_load), color = "orchid1", size = 1 ) + geom_line(data = mean_random_df, aes(x = generation, y = genetic_load), color = "yellow1", size = 1 )+ geom_line(data = mean_related_df, aes(x = generation, y = genetic_load), color = "skyblue1", size = 1 ) + geom_line(data = mean_mixed_df, aes(x = generation, y = genetic_load), color = "olivedrab3", size = 1 )+ labs(x = "Generations", y = "Genetic load") + theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 30),  # X-axis title size
    axis.title.y = element_text(size = 30),
    axis.text.x = element_text(size = 20),  # Increase x-axis label size
    axis.text.y = element_text(size = 20)# Increase axis title siz
  
  )
fitness_graph <- ggplot() + geom_line(data = mean_genload_df, aes(x = generation, y = fitness), color = "indianred1", size = 1 ) + geom_line(data = mean_rm_df, aes(x = generation, y = fitness), color = "orchid1", size = 1 ) + geom_line(data = mean_random_df, aes(x = generation, y = fitness), color = "yellow1", size = 1 )+ geom_line(data = mean_related_df, aes(x = generation, y = fitness), color = "skyblue1", size = 1 )+ geom_line(data = mean_mixed_df, aes(x = generation, y = fitness), color = "olivedrab3", size = 1 ) + labs(x = "Generations", y = "Fitness") + theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 30),  # X-axis title size
    axis.title.y = element_text(size = 30),
    axis.text.x = element_text(size = 20),  # Increase x-axis label size
    axis.text.y = element_text(size = 20)
        
  )

hetero_graph <- ggplot() + geom_line(data = mean_genload_df, aes(x = generation, y = heterozygosity), color = "indianred1", size = 1 ) + geom_line(data = mean_rm_df, aes(x = generation, y = heterozygosity), color = "orchid1", size = 1 ) + geom_line(data = mean_random_df, aes(x = generation, y = heterozygosity), color = "yellow1", size = 1 )+ geom_line(data = mean_related_df, aes(x = generation, y = heterozygosity), color = "skyblue1", size = 1 ) + geom_line(data = mean_mixed_df, aes(x = generation, y = heterozygosity), color = "olivedrab3", size = 1 )+ labs(x = "Generations", y = "heterozygosity") + theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 30),  # X-axis title size
    axis.title.y = element_text(size = 30),
    axis.text.x = element_text(size = 20),  # Increase x-axis label size
    axis.text.y = element_text(size = 20)
  )
ggsave(
  filename = paste0(path, "2_R-Workspace/Realizedload_plot.png"),  # Full file path
  plot = realized_graph,            # Plot object to save
  width = 7,              # Width in inches
  height = 10,             # Height in inches
  dpi = 600               # Resolution
)
ggsave(
  filename = paste0(path, "2_R-Workspace/totalload_plot.png"),  # Full file path
  plot = load_graph,            # Plot object to save
  width = 7,              # Width in inches
  height = 10,             # Height in inches
  dpi = 600               # Resolution
)
ggsave(
  filename = paste0(path, "2_R-Workspace/fitness_plot.png"),  # Full file path
  plot = fitness_graph,            # Plot object to save
  width = 7,              # Width in inches
  height = 10,             # Height in inches
  dpi = 600               # Resolution
)
ggsave(
  filename = paste0(path, "2_R-Workspace/hetero_plot.png"),  # Full file path
  plot = hetero_graph,            # Plot object to save
  width = 7,              # Width in inches
  height = 10,             # Height in inches
  dpi = 600               # Resolution
)


combined_plot <- load_graph + realized_graph + fitness_graph + hetero_graph + plot_layout(ncol = 4) + plot_annotation(theme = theme(plot.background = element_rect(fill = "#212121")))
ggsave(
  filename = paste0(path, "2_R-Workspace/combined_plot.png"),  # Full file path
  plot = combined_plot,            # Plot object to save
  width = 12,              # Width in inches
  height = 6,             # Height in inches
  dpi = 600               # Resolution
)
print(combined_plot)
```

plot the legend 

```{r}

library(cowplot)

# Create a dummy data frame for the legend
legend_data <- data.frame(
  x = c(1, 2, 3, 4),  # Dummy x-values
  y = c(1, 1, 1, 1),  # Dummy y-values
  group = factor(c("Minimize load", "Random mating related", "Random mating", "Relatedness"))  # Factor for legend
)

# Generate a plot with an enlarged legend
legend_plot <- ggplot(legend_data, aes(x = x, y = y, color = group)) +
  geom_point(size = 5) +  # Add dummy points for the legend
  scale_color_manual(
    values = c(
      "Minimize load" = "olivedrab3",
      "Random mating related" = "orchid1",
      "Random mating" = "yellow1",
      "Relatedness" = "skyblue1"
    )
  ) +
  labs(color = "Group Legend") +  # Set the legend title
  theme_minimal() +
  theme(
    legend.position = "bottom",          # Place the legend at the bottom
    legend.key.size = unit(2.5, "cm"),   # Increase size of legend keys
    legend.text = element_text(size = 16, color = "white"),  # Increase size of legend text
    legend.title = element_text(size = 18, color = "white"), # Increase size of legend title
    legend.key = element_rect(fill = "#212121"),  # #212121 background for legend keys
    panel.background = element_rect(fill = "#212121"),
    plot.background = element_rect(fill = "#212121"),
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank()
  )
# Extract only the legend part
legend_plot
```


```{r}
realized_graph_vs <- ggplot() + geom_line(data = mean_old_related_df, aes(x = generation, y = realized_load), color = "indianred1", size = 1 ) + geom_line(data = mean_related_df, aes(x = generation, y = realized_load), color = "skyblue1", size = 1 ) + labs(x = "Generations", y = "Realized load") + 
  theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 25),  # X-axis title size
    axis.title.y = element_text(size = 25),
    axis.text.x = element_text(size = 10),  # Increase x-axis label size
    axis.text.y = element_text(size = 10)# Increase axis title siz
  )

load_graph_vs <- ggplot() + geom_line(data = mean_old_related_df, aes(x = generation, y = genetic_load), color = "indianred1", size = 1 ) + geom_line(data = mean_related_df, aes(x = generation, y = genetic_load), color = "skyblue1", size = 1 ) + labs(x = "Generations", y = "total load") + theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 25),  # X-axis title size
    axis.title.y = element_text(size = 25),
    axis.text.x = element_text(size = 10),  # Increase x-axis label size
    axis.text.y = element_text(size = 10)# Increase axis title siz
  
  )
fitness_graph_vs <- ggplot() + geom_line(data = mean_old_related_df, aes(x = generation, y = fitness), color = "indianred1", size = 1 ) + geom_line(data = mean_related_df, aes(x = generation, y = fitness), color = "skyblue1", size = 1 ) + labs(x = "Generations", y = "fitness") + theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 25),  # X-axis title size
    axis.title.y = element_text(size = 25),
    axis.text.x = element_text(size = 10),  # Increase x-axis label size
    axis.text.y = element_text(size = 10)
        
  )

hetero_graph_vs <- ggplot() + geom_line(data = mean_old_related_df, aes(x = generation, y = heterozygosity), color = "indianred1", size = 1 ) + geom_line(data = mean_related_df, aes(x = generation, y = heterozygosity), color = "skyblue1", size = 1 ) + labs(x = "Generations", y = "heterozygosity")+ theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 25),  # X-axis title size
    axis.title.y = element_text(size = 25),
    axis.text.x = element_text(size = 10),  # Increase x-axis label size
    axis.text.y = element_text(size = 10)
  )
boomer_vs_genz_plot <- load_graph_vs + realized_graph_vs + fitness_graph_vs + hetero_graph_vs + plot_layout(ncol = 4) + plot_annotation(theme = theme(plot.background = element_rect(fill = "#212121")))
ggsave(
  filename = paste0(path, "2_R-Workspace/rel_old_vs_paper_plot.png"),  # Full file path
  plot = boomer_vs_genz_plot,            # Plot object to save
  width = 12,              # Width in inches
  height = 6,             # Height in inches
  dpi = 600               # Resolution
)
```

old vs paper mixed

```{r}
realized_graph_vs_mixed <- ggplot() + geom_line(data = mean_old_mixed_df, aes(x = generation, y = realized_load), color = "orchid", size = 1 ) + geom_line(data = mean_mixed_df, aes(x = generation, y = realized_load), color = "olivedrab3", size = 1 ) + labs(x = "Generations", y = "Realized load") + 
  theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 25),  # X-axis title size
    axis.title.y = element_text(size = 25),
    axis.text.x = element_text(size = 10),  # Increase x-axis label size
    axis.text.y = element_text(size = 10) 
  )

load_graph_vs_mixed <- ggplot() + geom_line(data = mean_old_mixed_df, aes(x = generation, y = genetic_load), color = "orchid", size = 1 ) + geom_line(data = mean_mixed_df, aes(x = generation, y = genetic_load), color = "olivedrab3", size = 1 ) + labs(x = "Generations", y = "total load") + theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 25),  # X-axis title size
    axis.title.y = element_text(size = 25),
    axis.text.x = element_text(size = 10),  # Increase x-axis label size
    axis.text.y = element_text(size = 10)
  )
fitness_graph_vs_mixed <- ggplot() + geom_line(data = mean_old_mixed_df, aes(x = generation, y = fitness), color = "orchid", size = 1 ) + geom_line(data = mean_mixed_df, aes(x = generation, y = fitness), color = "olivedrab3", size = 1 ) + labs(x = "Generations", y = "fitness") + theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 25),  # X-axis title size
    axis.title.y = element_text(size = 25),
    axis.text.x = element_text(size = 10),  # Increase x-axis label size
    axis.text.y = element_text(size = 10)
  )

hetero_graph_vs_mixed <- ggplot() + geom_line(data = mean_old_mixed_df, aes(x = generation, y = heterozygosity), color = "orchid", size = 1 ) + geom_line(data = mean_mixed_df, aes(x = generation, y = heterozygosity), color = "olivedrab3", size = 1 ) + labs(x = "Generations", y = "heterozygosity")+ theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white"),
    axis.title.x = element_text(size = 25),  # X-axis title size
    axis.title.y = element_text(size = 25),
    axis.text.x = element_text(size = 10),  # Increase x-axis label size
    axis.text.y = element_text(size = 10)
  )
boomer_vs_genz_plot_mixed <- load_graph_vs_mixed + realized_graph_vs_mixed + fitness_graph_vs_mixed + hetero_graph_vs_mixed + plot_layout(ncol = 4) + plot_annotation(theme = theme(plot.background = element_rect(fill = "#212121")))
ggsave(
  filename = paste0(path, "2_R-Workspace/mixed_old_vs_paper_plot.png"),  # Full file path
  plot = boomer_vs_genz_plot_mixed,            # Plot object to save
  width = 12,              # Width in inches
  height = 6,             # Height in inches
  dpi = 600               # Resolution
)
```



# Statistical analysis

## Student t test within each regimes between the hundreds replicates

```{r}

# loading the end points for every replicates
end_random_related <- rm_df[rm_df$Generation == 101,]
end_random <- random_df[random_df$Generation == 101,]
end_load <- genload_df[genload_df$Generation == 101,]
end_related <- related_df[related_df$Generation == 101,]
end_mixed <- mixed_df[mixed_df$Generation == 101,]
```

```{r}
batch_ttest_load <- t.test(end_load$RelzLoad) ; batch_ttest_load
batch_ttest_random <- t.test(end_random$RelzLoad) ; batch_ttest_random
batch_ttest_random_related <- t.test(end_random_related$RelzLoad) ; batch_ttest_random_related
batch_ttest_related <- t.test(end_related$RelzLoad) ; batch_ttest_related
batch_ttest_mixed <- t.test(end_mixed$RelzLoad) ; batch_ttest_mixed
```

## Anova between all the regimes 100 batches

```{r}

end_load$regime <- "load"
end_random_related$regime <- "random_related"
end_random$regime <- "random"
end_related$regime <- "related"
end_mixed$regime <- "mixed"
model_df <- as.data.frame(rbind(end_load, end_mixed, end_random, end_random_related, end_related))
model_df$regime <- factor(model_df$regime)
```

analysis on realized load

```{r}
library("reshape2")
mod <- aov(model_df$MeanFitness ~ model_df$regime)
anova(mod)
posthoc <- TukeyHSD(mod)
print(posthoc)

tukey_df <- as.data.frame(posthoc$`model_df$regime`)
tukey_df$Comparison <- rownames(tukey_df)

tukey_df$Significance <- ifelse(tukey_df$`p adj` <= 0.05, "*", "")  # Add "*" for p <= 0.05

# Plot with stars for significant points
post_hoc_graph <- ggplot(tukey_df, aes(x = reorder(Comparison, diff), y = diff)) +
  geom_point(size = 3, color = "white") +
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = 0.3, color = "white") +
  geom_text(aes(label = Significance), nudge_x = 0.3, color = "red", size = 5) + # Add stars
  labs(
    title = "Tukey Post-Hoc Test Results",
    x = "Pairwise Comparisons",
    y = "Mean Difference"
  ) +
  coord_flip() + # Rotate for better readability
  theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_line(color = "gray50"),
    panel.grid.minor = element_line(color = "gray50"),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white", size = 30),
    axis.title.x = element_text(size = 20),  # X-axis title size
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 15),  # Increase x-axis label size
    axis.text.y = element_text(size = 15)
  )

print(post_hoc_graph)
ggsave(
  filename = paste0(path, "2_R-Workspace/post_hoc_graph.png"),  # Full file path
  plot = post_hoc_graph,            # Plot object to save
  width = 10,              # Width in inches
  height = 7,             # Height in inches
  dpi = 600               # Resolution
)

tukey_df$Group1 <- sapply(strsplit(rownames(tukey_df), "-"), `[`, 1)  # Split comparisons
tukey_df$Group2 <- sapply(strsplit(rownames(tukey_df), "-"), `[`, 2)  # Split comparisons

# Create a matrix-like data frame for heatmap
heatmap_data <- reshape2::dcast(tukey_df, Group1 ~ Group2, value.var = "p adj")
heatmap_data[is.na(heatmap_data)] <- 1  # Replace NAs with 1 (non-significant p-values)

# Melt the data frame for ggplot
heatmap_melt <- reshape2::melt(heatmap_data, id.vars = "Group1")

# Add a new column for significance (red for p <= 0.05, grey otherwise)
heatmap_melt$Significance <- ifelse(heatmap_melt$value <= 0.05, "Significant", "Not Significant")

# Plot the heatmap
heatmap_pvalue <- ggplot(heatmap_melt, aes(x = Group1, y = variable, fill = Significance)) +
  geom_tile(color = "white") +
  scale_fill_manual(
    values = c("Significant" = "red", "Not Significant" = "grey"),
    name = "Significance"
  ) +
  labs(
    title = "Heatmap of Tukey Test Results",
    x = "Group 1",
    y = "Group 2"
  ) +
    theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_line(color = "gray50"),
    panel.grid.minor = element_line(color = "gray50"),
    legend.title = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white", size = 10),
    axis.title.x = element_blank(),  # X-axis title size
    axis.title.y = element_blank(),
    axis.text.x = element_text(size = 20),  # Increase x-axis label size
    axis.text.y = element_text(size = 20)
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave(
  filename = paste0(path, "2_R-Workspace/heatmap_pvalue.png"),  # Full file path
  plot = heatmap_pvalue,            # Plot object to save
  width = 10,              # Width in inches
  height = 7,             # Height in inches
  dpi = 600               # Resolution
)
```


Analysis on Heterozygosity 

```{r}
mod <- aov(model_df$Heterozygosity ~ model_df$regime)
anova(mod)
posthoc <- TukeyHSD(mod)
print(posthoc)

tukey_df <- as.data.frame(posthoc$`model_df$regime`)
tukey_df$Comparison <- rownames(tukey_df)

tukey_df$Significance <- ifelse(tukey_df$`p adj` <= 0.05, "*", "")  # Add "*" for p <= 0.05

# Plot with stars for significant points
post_hoc_graph <- ggplot(tukey_df, aes(x = reorder(Comparison, diff), y = diff)) +
  geom_point(size = 3, color = "white") +
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = 0.3, color = "white") +
  geom_text(aes(label = Significance), nudge_x = 0.3, color = "red", size = 5) + # Add stars
  labs(
    title = "Tukey Post-Hoc Test Results",
    x = "Pairwise Comparisons",
    y = "Mean Difference"
  ) +
  coord_flip() + # Rotate for better readability
  theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_line(color = "gray50"),
    panel.grid.minor = element_line(color = "gray50"),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white", size = 30),
    axis.title.x = element_text(size = 20),  # X-axis title size
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 15),  # Increase x-axis label size
    axis.text.y = element_text(size = 15)
  )

print(post_hoc_graph)
ggsave(
  filename = paste0(path, "2_R-Workspace/post_hoc_graph_hetero.png"),  # Full file path
  plot = post_hoc_graph,            # Plot object to save
  width = 10,              # Width in inches
  height = 7,             # Height in inches
  dpi = 600               # Resolution
)

tukey_df$Group1 <- sapply(strsplit(rownames(tukey_df), "-"), `[`, 1)  # Split comparisons
tukey_df$Group2 <- sapply(strsplit(rownames(tukey_df), "-"), `[`, 2)  # Split comparisons

# Create a matrix-like data frame for heatmap
heatmap_data <- reshape2::dcast(tukey_df, Group1 ~ Group2, value.var = "p adj")
heatmap_data[is.na(heatmap_data)] <- 1  # Replace NAs with 1 (non-significant p-values)

# Melt the data frame for ggplot
heatmap_melt <- reshape2::melt(heatmap_data, id.vars = "Group1")

# Add a new column for significance (red for p <= 0.05, grey otherwise)
heatmap_melt$Significance <- ifelse(heatmap_melt$value <= 0.05, "Significant", "Not Significant")

# Plot the heatmap
heatmap_pvalue <- ggplot(heatmap_melt, aes(x = Group1, y = variable, fill = Significance)) +
  geom_tile(color = "white") +
  scale_fill_manual(
    values = c("Significant" = "red", "Not Significant" = "grey"),
    name = "Significance"
  ) +
  labs(
    title = "Heatmap of Tukey Test Results",
    x = "Group 1",
    y = "Group 2"
  ) +
    theme(
    plot.background = element_rect(fill = "#212121"),
    panel.background = element_blank(),
    panel.grid.major = element_line(color = "gray50"),
    panel.grid.minor = element_line(color = "gray50"),
    legend.title = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white", hjust = 0.5),
    legend.background = element_rect(fill = "#212121"),
    legend.text = element_text(color = "white", size = 10),
    axis.title.x = element_blank(),  # X-axis title size
    axis.title.y = element_blank(),
    axis.text.x = element_text(size = 20),  # Increase x-axis label size
    axis.text.y = element_text(size = 20)
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave(
  filename = paste0(path, "2_R-Workspace/heatmap_pvalue_hetero.png"),  # Full file path
  plot = heatmap_pvalue,            # Plot object to save
  width = 10,              # Width in inches
  height = 7,             # Height in inches
  dpi = 600               # Resolution
)
```















